The contact value approximation for the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-06-13 papers/pair-correlation/paper.tex

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figs/ghs-alt}
  \caption{Plot of the hard-sphere radial distribution function. The blue
    lines show our separable fit, the black dots are Monte Carlo data, and
    the dashed lines are results of the Gil-Villegas\cite{gil1997statistical}
    fit.\pahosays{An idea for an alternate version of the radial distribution
      figure.}}\label{fig:radial-distribution-alt}
\end{figure}
